---
title: "p8105_mtp_bg2715"
author: "Baode Gao"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
#library(rvest)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Introduction

## Problem 1
Import and clean the data.
```{r}
eop_df = 
  readxl::read_excel("./p8105_mtp_data.xlsx",  range = "A9:I1230") %>%
  janitor::clean_names() %>%
  rename(eop_size_type = eop_size) %>%
  replace_na(list(eop_size_mm = 0)) %>%
  replace_na(list(eop_shape = 0)) %>%
  mutate(
    sex = recode(sex, "0" = "female", "1" = "male"
    ),
    age_group = recode(age_group, "2" = "18-30",
                       "3" = "31-40","4" = "41-50",
                       "5" = "51-60", "6" = "60+", 
                       "7" = "60+","8" = "60+"
    ),
    eop_size_type = recode(eop_size_type, "0" = "0-5",
                           "1" = "5-10",  "2" = "10-15",
                           "3" = "15-20", "4" = "20-25",
                           "5" = "25+"
    ),
    fhp_category = recode(fhp_category, "0" = "0-10", "1" = "10-20",
                          "2" = "20-30", "3" = "30-40",
                          "4" = "40-50", "5" = "50-60",
                          "6" = "60-70", "7" = "70-80"
    ),
    sex = factor(sex),
    eop_size_type = factor(eop_size_type),
    eop_visibility_classification =
      factor(eop_visibility_classification),
    fhp_category = factor(fhp_category),
    age_group = factor(age_group),
  )


```
I replaced the missing value by zero and converted categorical variables from numeric variable to character and factors. Based on the paper, key variables include 'age', 'sex' and 'fhp_category'. There are 1221 observations.

Age and gender distribution.
```{r}
agesex_df = eop_df %>% 
  select(sex, age_group) %>% 
  group_by(age_group) %>% 
  count(sex, name = "count")
knitr::kable(agesex_df)
```
Different gender have same trend within age groups. 18-30 and 60+ age groups are more than other groups.
```{r}
issues_df = 
  readxl::read_excel("./p8105_mtp_data.xlsx",  range = "A9:I1230") %>%
  janitor::clean_names() %>%
  rename(eop_size_type = eop_size) %>%
  replace_na(list(eop_size_mm = 0)) %>%
  replace_na(list(eop_shape = 0)) %>%
  filter(!(age_group %in% c(2,3,4,5,6,7,8))|
         !(eop_size_type %in% c(0,1,2,3,4,5))|
         !(fhp_category %in% c(0,1,2,3,4,5,6,7))|
         !(eop_visibility_classification %in% c(0,1,2))|
         !(sex %in% c(0,1))
           )
knitr::kable(issues_df)
```
There are two observations with age_group 1, one observation with eop_size_type 14.6 and one observation with fhp_category 30.8, which are meaningless. 
